---
title: "Calgary Ultee Field Locations"
author: "Murray Thompson"
date: "April 14, 2017"
output: html_document
---


## Background

As this assignment required incorporating a map, I decided to try and take a custom Google map I created a few years agao, and see how I could translate it from the exported KML to a Leaflet-based map.

The orginal map can be found here:
https://www.google.com/maps/d/edit?mid=17Z8P2QTdKv4J72iCMgGTgSSHj1g&ll=51.064620084093576%2C-114.16622367275994&z=15

*Note: in case you play Ultimate in Calgary, this map may now be out of date :)*

## Preparation
```{r}

# load libraries
library(XML)
library(tidyr)
library(leaflet)
# library(htmlwidgets)

```

## Open and process the exported KML document:

```{r echo=TRUE}
  kmlDoc <- xmlParse("fieldmapdata.kml")
  fieldMapPlacemarks = xmlToDataFrame(getNodeSet(kmlDoc, "//k:Placemark", c(k="http://www.opengis.net/kml/2.2")))
  
  fieldMapPlacemarks <- separate(fieldMapPlacemarks, Point, c("Long", "Lat","Elev"), sep=",", remove=TRUE, convert=TRUE)
  fieldMapPlacemarks$styleUrl <- NULL
```

Note that this KML document only contains placemarks in a signle layer, and not lines or areas. It also does not retain the custom symbols for each location that are displayed in the orginal Google map.

## The map:

```{r echo=TRUE}

map <- leaflet() %>%
  addTiles() %>%
  addMarkers(lng=fieldMapPlacemarks$Long, lat=fieldMapPlacemarks$Lat, label=fieldMapPlacemarks$name, popup=fieldMapPlacemarks$description)

map

```